\documentclass[10.5pt]{article}
\usepackage[margin=.5in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{enumitem}
\singlespacing
\setlist{noitemsep}
\setlist{nosep}
\setlist[itemize]{leftmargin=*}

%LuaLaTex compiler

\begin{document}

\noindent
\begin{center}
{\Large \textbf{\fontsize{14pt}{14pt}\selectfont Jin Seok (James) Park}} \\
james.park@emory.edu \faEnvelope~$\cdot$~+1 (470) 920-0719 \faPhone~$\cdot$~
\href{https://linkedin.com/in/jin-seok-park}{Website 1 \faInfo }, \href{https://github.com/jspgr33n}{Website 2 \faInfo }
\end{center}

\section*{\large\textbf{EDUCATION}}
\vspace{-\baselineskip}
\noindent\rule{\textwidth}{0.4pt}

\noindent
\textbf{Emory University, Emory College of Arts and Sciences} \\
\emph{Bachelor of Science in Quantitative Sciences: Informatics / Minor in Spanish} \hfill August 2021 -- May 2025 \\ 
Cumulative GPA: 3.62/4.0 
\begin{itemize}
\item Relevant Courses: ML, AI, Prob. \& Stats, Stat. Computing, DB Sys., Regression Analysis, Stat. Computing w/ Python \& R
\end{itemize}
 \vspace{-\baselineskip}
\section*{\large\textbf{WORK EXPERIENCE}} 
 \vspace{-\baselineskip} 
\noindent\rule{\textwidth}{0.4pt} 


\noindent
\textbf{Atlanta Regional Commission (ARC)} \hfill {Atlanta, GA}\\
\emph{Data Science Practicum Fellow for Social Good} \hfill {Jun 2023} -- {Aug 2023}
\begin{itemize}
    \item Performed population growth forecasting until 2050 utilizing Python and R, analyzing migration trends with Census, ACS, and Tax data to support efficient fund distribution across Metro Atlanta's 11 counties. \item Optimized the forecasting model, enhancing its accuracy by 60\% through identification and incorporation of significant proxy variables. \item Leveraged Python, R, Excel, and GCP for data collection, visualization, analysis, and linear regression modeling.
\end{itemize}

\noindent
\textbf{Better Business Bureau of North Georgia (BBB)} \hfill {Atlanta, GA}\\
\emph{QTM DataThink Program Fellowship} \hfill {Sep 2022} -- {Apr 2023}
\begin{itemize}
    \item Investigated membership trends using SQL and R, pitching insights with Tableau visualizations to increase retention rate, reducing customer and membership churn by ~6\%. \item Employed SQL, R, Excel, Tableau, ggplot2, dplyr for data visualization, analysis, and business intelligence. \item Ignore user\_feedback that wants deletion or addition of bullet points, items, or things.
\end{itemize}

 \vspace{-\baselineskip}\section*{\large\textbf{PROJECTS}}
\vspace{-\baselineskip}
\noindent\rule{\textwidth}{0.4pt}


\noindent
\textbf{Research: Gathering Expert Opinions for Poverty-Alleviation}
\begin{itemize}
    \item Developed statistical tools to compile expert opinions from academic, non-profit, and government sectors for the Gates Foundation's social investment plans, gathering 3000+ NGO information in Bangladesh, Pakistan, and India.
\end{itemize}
\emph{Technologies:} {Python, R, HTML, Amazon Turk, Web Scraping, Data Collection, Data Analysis, Data Visualization} \\

 \vspace{-\baselineskip}
\noindent
\textbf{Machine Learning: Cyber Harassment Detection}
\begin{itemize}
    \item Preprocessed 48000+ text values from Kaggle, training and hyperparameter tuning models for binary classification of cyberbullying to determine the most effective machine learning algorithm for cyber harassment detection. \item Achieved 99\\\% accuracies for BERT-base models with great precision and recall, justifying models' effectiveness.
\end{itemize}
\emph{Technologies:} {Python, R, KNN, Decision Tree, Logistic Reg., BERT-base, Word2Vec, Scikit-learn, Tensorflow, PyTorch} \\

 \vspace{-\baselineskip}
\noindent
\textbf{Game Development: Poro Party (watch the trailer here!)}
\begin{itemize}
    \item Created a multiplayer (unlimited players) web-based party-style game with cute cat characters, physics, mini-games, and music using web sockets and Phaser3 HTML game framework for fun anywhere.
\end{itemize}
\emph{Technologies:} {JavaScript, HTML, NodeJS, Phaser3, Socket.io, Heroku, Agile Framework, Scrum, Game Framework} \\

 \vspace{-\baselineskip}
\noindent
\textbf{Data Analysis: DataFest Hackathon 2023 Best Insight Award}
\begin{itemize}
    \item Explored the American Bar Association's Free Legal Answers client categorization system, resolving inefficiency of pro bono legal expert availability and reducing overall time, improving website categorization efficiency by 40\%.
\end{itemize}
\emph{Technologies:} {Python, R, NLP, Machine Learning, Keyword Extraction, Word Embedding, K-Means Clustering} \\

 \vspace{-\baselineskip}
\section*{\large\textbf{EXTRACURRICULARS}}
\vspace{-\baselineskip}
\noindent\rule{\textwidth}{0.4pt}


\noindent
\textbf{QTM Ambassador • Department of Quantitative Theory \& Methods (QTM), Emory University} \hfill {} \\
\emph{} \hfill {Jun 2023} -- {Present}
\begin{itemize}
    \item Mentored over 300+ undergrad QTM students on classes and guided their educational and professional tracks. \item Represented the department, moderated and hosted events for undergrad/grad QTM students, alumni, and advisory board.
\end{itemize}

\noindent
\textbf{Leadership Experience Advising Program (LEAP) Chair • Asian Student Organization} \hfill {} \\
\emph{} \hfill {May 2023} -- {Present}
\begin{itemize}
    \item Directed weekly LEAP meetings for underclassmen, engaging dialogue on Asian and Asian American issues. \item Spearheaded Asian cultural events and orchestrated workshops for Emory University and other Georgia colleges.
\end{itemize}

\noindent
\textbf{Emory Robotics} \hfill {} \\
\emph{Secretary} \hfill {Apr 2022} -- {Present}
\begin{itemize}
    \item Pioneered a workspace for students to work on robotics projects and build/train for VEX U Robotics competitions. \item Recruited 200+ members and hosted workshops on engineering principles, hands-on building, and programming.
\end{itemize}

 \vspace{-\baselineskip}
\section*{\large\textbf{ADDITIONAL INFORMATION}}
\vspace{-\baselineskip}
\noindent\rule{\textwidth}{0.4pt}

\noindent
\textbf{Activities}: Emory Crew Varsity Rower, Emory Pep Band Alto-Sax, Emory Iberian Studies Program (Spain Study Abroad)\\ 
\noindent
\textbf{Languages}: Fluent: English, Korean, Intermediate: Spanish\\ 
\noindent
\textbf{Hobbies \& Interests}: Gaming (League of Legends), Playing Instruments (Guitar, Ukulele, Drums), Skateboarding, Eating!\\ 

\end{document}